---
title: "Analysis of Marriage Licence Statistics in Toronto from 2011 to 2024"
subtitle: "My subtitle if needed"
author: 
  - Jiwon Choi
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "This analysis examines marriage registration trends in Toronto from 2011 to 2024, with a focus on comparing the periods before and after the COVID-19 pandemic. The data includes the number of marriage licenses issued across four key civic centres: Toronto, North York, Etobicoke, and Scarborough. By analyzing these trends, we aim to understand the impact of the pandemic on marriage registrations, reflecting potential shifts in social behavior during and after the crisis."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

Talk more about it.


# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


